\documentclass{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{url}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Check these macro values for appropriateness for your own document.

\title{IS3 Group Report}

%%authors
\author{
  Richard Fleming \\
  James Gallagher \\
  Craig McLaughlin \\
  Victor Pantazi \\
  Gordon Reid}

%%release date 
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Standard section for all documents

\section{Preamble}

\subsection{In This Report}

\begin{itemize}
\item Give an overview of your paper prototypes, the early designs and
how you came to your final prototype design;

\item Explain how they work;

\item Report on your heuristic evaluation/think aloud, any problems you
found and how you resolved them (include the key paper prototypes that
you built);

\item Make a simple video of your final prototype (video from a phone
is fine) upload it to a video sharing site so we can see it in action.
I am not expecting Hollywood quality, but just enough to get an idea
of how your system would work. You can get some inspiration from the
video above;

\item Once your video is publicly available, send the link out to
friends and family and get them to comment in the public area and use
that information to create suggestions for improving the design.
\end{itemize}

\section{Overview}

Insert references in this text for the different calendars if they
have websites.

Our prototypes were based on the Facebook, Calendar for OS X,
Evolution on Scientific Linux and Google Calendars. For prototyping and
evaluating we split up into two person teams. For the purposes of the
discussion the teams are labelled based on the calendars they
evaluated.

\subsection{Calendar on OS X}

Paper prototype has minimalist design with four views: day, week, month
and year. These views are available through four buttons that are
always on the screen at the top center-right of the screen. The
currently selected view is colour/depressed differently than the
others.

%%%%%%%%%

See figures (need figures).
\section{The Video}

Video Link here.

%% Separate sections with line of comment symbols.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
